---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# carpriceprediction

<!-- badges: start -->
![](https://github.com/uliaLiao/dsci-310-group-07-pkg/actions/workflows/test-coverage.yaml/badge.svg)
![](https://codecov.io/gh/uliaLiao/dsci-310-group-07-pkg/branch/main/graph/badge.svg)
<!-- badges: end -->

This package is designed to assist in the exploration and visualization of data related to car attributes such as make, length, and other important factors that can affect pricing. The functions within the package allow users to preprocess the data, perform regression analysis, and evaluate model performance. 


## Installation

You can install the development version of carpriceprediction from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-07-pkg")
```

## Usage

In order to use the functions in the package, load the `carpriceprediction` library:

```{r example}
library(carpriceprediction)
```

### Data

In this example, we will use the actual `automobile` dataset. And the first 6 lines of `automobile` is as follows:

```{r load-automobile, echo=FALSE}
data("automobile")
head(automobile)
```

### EDA

```{r getR2}
(getR2(automobile,n = 2))
```


```{r plotAll, message=FALSE, warning=FALSE}
plots <- plotAll(automobile, c("make","engine-size"))
# `make` is a factor, hence show the barplot
plots[[1]]
```

```{r plotAll-cont, message=FALSE, warning=FALSE}
# `engine-size` is continuous, henshow show the histogram and scatterplot with a linear regression line
plots[[2]]
plots[[3]]
```

### Fit models

```{r get_tr_tst, eval=TRUE}

# By specifying the set = "basic", the result contains all columns
training_df<-get_tr_tst(automobile,"basic")[[1]]
testing_df<-get_tr_tst(automobile,"basic")[[2]] 

# By specifying the set = "at", the result contains all columns except ID
training_df_at<-get_tr_tst(automobile,"at")[[1]]
testing_df_at<-get_tr_tst(automobile,"at")[[2]]

# By specifying the set = "sub", the result contains columns except ID or categorical variables with more than 2 levels
training_df_sub<-get_tr_tst(automobile,"sub")[[1]]
testing_df_sub<-get_tr_tst(automobile,"sub")[[2]] 

```


```{r get_trm_tsm, eval=TRUE}
# training matrices
training_matrices <- get_trm_tsm(training_df_sub, 
                                 testing_df_sub, 
                                 set = "training")
x_train_mat <- training_matrices[[1]]
y_train_mat <- training_matrices[[2]]

# testing matrices
testing_matrices <- get_trm_tsm(training_df_sub, 
                                testing_df_sub, 
                                set = "testing")
x_test_mat <- testing_matrices[[1]]
y_test_mat <- testing_matrices[[2]]

```

Lasso regression:

```{r lasso, eval=TRUE}
# Lasso regression
lasso_mods <-
  get_model_plot(x_train_mat, 
                 y_train_mat, 
                 model = "lasso", 
                 ask = "modeling")

# model with lambda resulting in minimum mse
lasso_mod <- lasso_mods[[1]]

# model with lambda resulting in (minimum mse + 1SE)
lasso_mod_1se <- lasso_mods[[2]]

# Training results with all lambdas
lasso_cv <- lasso_mods[[3]]

# visualize lasso_cv:
# get_model_plot(x_train_mat, y_train_mat, model = "lasso", ask = "plot")

```

Ridge regression:

```{r ridge,eval=TRUE}
ridge_mods <-
  get_model_plot(x_train_mat, 
                 y_train_mat, 
                 model = "ridge", 
                 ask = "modeling")

# model with lambda resulting in minimum mse
ridge_mod <- ridge_mods[[1]]

# model with lambda resulting in (minimum mse + 1SE)
ridge_mod_1se <- ridge_mods[[2]]

# Training results with all lambdas
ridge_cv <- ridge_mods[[3]]

# visualize ridge_cv:
# get_model_plot(x_train_mat, y_train_mat, model = "ridge", ask = "plot")
```

Performance of different models:

```{r err,eval=TRUE}
get_er_cv(training_df_at, training_df_sub, kfolds = 10, lasso_cv, ridge_cv)
```

## Code of Conduct

Please note that the carpriceprediction project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


