---
title: "carpriceprediction EDA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{eda-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This vignette contains examples and documentation on how to use **carpriceprediction** package to perform exploratory data analysis (EDA) on the **automobile** dataset, which was created by Jeffrey C. Schlimmer in 1985. The data were collected from [imports-85](https://archive.ics.uci.edu/ml/machine-learning-databases/autos/imports-85.data).

Before EDA, you can obtain the data by either 

* reading the data from [imports-85](https://archive.ics.uci.edu/ml/machine-learning-databases/autos/imports-85.data), or
* using the [automobile.rds](https://github.com/uliaLiao/dsci-310-group-07-pkg/blob/main/saved/automobile.rds), which is saved as an R object, all the categorical variables are read as factors and all missing values are replaced as `NA`s. 

With this package, you will be able to

* save variables that help generating the report;
* obtain the first `n` variables that explain most variations of the `price`.
* visualize the distribution of these `n` variables across dataset. 

## Data

The **automobile** dataset contains 26 rows and 205 observations. The response variable is `price` and the others are explanatory variables. In this example, the dataset is loaded by `readRDS()` from *base R*.

```{r load-automobile, eval=FALSE}
#install.packages('here')
automobile <- readRDS(here::here("saved/automobile.rds"))
head(automobile)
```


```{r setup}
library(carpriceprediction)

```

## Functions

The function `saveVar()` allows you to save the column `price` as a `.rds` file. The `name` should end with `.rds` and cannot be empty, or it may cause error.


```{r saveVar, eval=FALSE}
saveVar(var = automobile$price, name = "price.rds", out_dir = "result")
# will print "price.rds saved to your/absolute/path/.../result"
# will return "price.rds saved to result"

```

The function `getR2()` allows you to get $R^2$ of the first `n` explanatory variables that explain most variations by fitting OLS model. The input variable `n` should be whole numbers from 1 to 25.

```{r getR2, eval=FALSE}
(getR2(dat = automobile,n = 2))
```

The function `plotAll()` visualize the distribution of chosen variables in `automobile`. The function returns a list of plots.

* `make` is a factor, hence presents the barplot.
* `engine-size` is continuous, hence presents the histogram and scatterplot with a linear regression line. One continuous variable takes two slots in the returned list.

```{r plotAll, message=FALSE, warning=FALSE, fig.width=6,fig.height=5, eval=FALSE}
plots <- plotAll(automobile, c("make","engine-size"))
# access barplot for "make"
plots[[1]]
# access histogram for "engine-size"
plots[[2]]
# access scatterplot for "engine-size"
plots[[3]]


```


